Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-01-16 paper/manuscript.Rmd
update figures / reflected feedback
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r set-up, include = FALSE}
if (!require("papaja")) {install.packages("papaja"): require("papaja")}
if (!require("here")) {install.packages("here"): require("here")}
if (!require("magick")) {install.packages("magick"): require("magick")}
if (!require("ggsci")) {install.packages("ggsci"): require("ggsci")}
```

@@

Effective teaching involves experts and novices dynamically interacting with each other [@byrne_2011]. First, experts demonstrate what novices are meant to acquired and then novices attempt to reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities [@mermelshtine_2017]. This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by identifying novices' specific problems of each novice from their unsuccessful attempts and modifying their behaviour accordingly [@ugur_2015; @zukow-goldring_2007].

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions [@pezzulo_2019], including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared to when they were demonstrating to adults [@brand_2002].Such pedagogical action modulations are sensitive to the skill level of learners. For instance, evidence from parental scaffolding research suggests that caregivers scaffold infants’ learning when the infants failed to produce an expected action [@wood_1975; @zukow-goldring_2007]. @fukuyama_2015 performed a study, where mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups of different colours and sizes. Mothers demonstrated how to stack and fit the nesting cups with the intention to teach their infants to reproduce the actions by themselves. It was found that the mothers dynamically modulated their demonstrations according to the infants' object manipulation skills. Specifically, mothers exaggerated their movements when their infants failed to produce expected actions but did not produce such exaggerations when their infants lacked the motor skills needed to produce the required actions. Movement exaggerations for the purpose of teaching are observed not only towards infant learners but also when knowledgeable adults are interacting with adult learners [@mcellin_2017]. For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own. However, it has not been established whether and how experts teaching skills to adult learners adjust their demonstrations as a function of the learners’ demonstrated skills.

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research [@tominaga_2022], we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To gain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., in press). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

The recorded performances serving as stimuli were all of one piece of music that had already been used in our previous study (Tominaga et al., in press). The piece was an excerpt from Clementi's Sonatina Op.36 (No.3) in C major. The first 12 measures of the original piece were used and modified so that the piece had an almost equal number of data points (i.e., the number of notes, the number of intervals between notes) for each dependent variable. The modified piece consisted of a 12-measure isochronous melody notated in 4/4 meter to be played with the right hand only. Two expressive notations (i.e., articulation and dynamics) were added, as shown in *Fig \ref{fig:stim}*.

@@

As predicted, experts produced longer legato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, left). Accordingly, here was a significant main effect of Articulation (*F*(`r leg_all_aov$anova_table[1,1]`, `r leg_all_aov$anova_table[1,2]`) = `r leg_all_aov$anova_table[1,4]`, *p* `r if(leg_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', leg_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[1,5])`). There was no significant main effect of Dynamics (*F*(`r leg_all_aov$anova_table[2,1]`, `r leg_all_aov$anova_table[2,2]`) = `r leg_all_aov$anova_table[2,4]`, *p* `r if(leg_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r leg_all_aov$anova_table[3,1]`, `r leg_all_aov$anova_table[3,2]`) = `r leg_all_aov$anova_table[3,4]`, *p* `r if(leg_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[3,5])`).

@@

```{r kot-plot-1, include = FALSE}
leg_all_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-20, 140, 40), limits = c(-20, 140)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

sta_all_plot <- ggplot(kot[Subcomponent1 == "Staccato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Staccato") + scale_y_continuous(breaks = seq(-280, -120, 40), limits = c(-280, -120)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

Unlike our prediction, experts did not change their performances in terms of notated forte depending on the type of recordings (*Fig \ref{fig:vel-1}*, left). Neither the main effect of Articulation (*F*(`r for_all_aov$anova_table[1,1]`, `r for_all_aov$anova_table[1,2]`) = `r for_all_aov$anova_table[1,4]`, *p* `r if(for_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', for_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.2f', for_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r for_all_aov$anova_table[2,1]`, `r for_all_aov$anova_table[2,2]`) = `r for_all_aov$anova_table[2,4]`, *p* `r if(for_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r for_all_aov$anova_table[3,1]`, `r for_all_aov$anova_table[3,2]`) = `r for_all_aov$anova_table[3,4]`, *p* `r if(for_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[3,5])`).

@@

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., expert pianists should modulate their performance relevant to articulation, but not dynamics).

@@

Artificial recordings were generated from performance data that we obtained in our previous study (Tominaga et al., in press). We used the data from Experiment 2. In Experiment 2, participants were asked to memorise one piece of music (*Fig 5* (A), Tominaga et al., in press) without any expressive notation before coming to the experiment. First, we asked participants to perform the memorised piece before starting the experiment to measure their baseline performance. After measuring the baseline performance, participants were asked to perform the piece with either articulation (*Fig 5* (B), Tominaga et al., in press) or dynamics (*Fig 5* (C), Tominaga et al., in press) in two conditions (teaching vs. performing). Here, we only used the data from the performing condition to make sure that the performances that we used did not have any particular modulations because of teaching intentions. Therefore, there were two types of performance data (articulation performance: performances played with notated articulation, dynamics performance: performances played with notated dynamics). We obtained 31 valid performances (i.g., performances without pitch errors) as baseline performances, 137 valid performances as articulation performances and 139 valid performances as dynamics performances.

@@

We aimed to generate four types of recordings and each type (i.e., both, art only, dyn only, none) had four instances (see *Apparatus and stimuli*) by using the performance data from Tominaga et al (in press). First, 16 instances for each type were generated. Second, for each type, we chose the four best instances, which exhibited the characteristic of each type well.

>>>>

```{r set-up, include = FALSE}
if (!require("papaja")) {install.packages("papaja"): require("papaja")}
if (!require("here")) {install.packages("here"): require("here")}
if (!require("magick")) {install.packages("magick"): require("magick")}
if (!require("ggsci")) {install.packages("ggsci"): require("ggsci")}
if (!require("ggsignif")) {install.packages("ggsignif"): require("ggsignif")}
```

@@

Effective teaching involves experts and novices dynamically interacting with each other [@byrne_2011]. First, experts demonstrate what novices are meant to acquire and then novices attempt to reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities [@mermelshtine_2017]. This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by identifying novices' specific problems from their unsuccessful attempts and modifying their behaviour accordingly [@ugur_2015; @zukow-goldring_2007].

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions [@pezzulo_2019], including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and to produce wide and expansive movements compared to when they were demonstrating to adults [@brand_2002]. Such pedagogical action modulations are sensitive to the skill level of learners. For instance, evidence from parental scaffolding research suggests that caregivers scaffold infants’ learning when the infants failed to produce an expected action [@wood_1975; @zukow-goldring_2007]. @fukuyama_2015 performed a study, where mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups of different colours and sizes. Mothers demonstrated how to stack and fit the nesting cups with the intention to teach their infants to reproduce the actions by themselves. It was found that mothers dynamically modulated their demonstrations according to the infants' object manipulation skills. Specifically, mothers exaggerated their movements when their infants failed to produce expected actions but did not produce such exaggerations when their infants lacked the motor skills to produce the required actions. Movement exaggerations for the purpose of teaching are observed not only towards infant learners but also when knowledgeable adults are interacting with adult learners [@mcellin_2017]. For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own. However, it has not been established whether and how experts teaching skills to adult learners adjust their demonstrations as a function of the learners’ demonstrated skills.

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on learners' skill level. In our previous research [@tominaga_2022], we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To obtain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study [@tominaga_2022]. All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

The recorded performances serving as stimuli were all of one piece of music that had already been used in our previous study [@tominaga_2022]. The piece was an excerpt from Clementi's Sonatina Op.36 (No.3) in C major. The first 12 measures of the original piece were used and modified so that the piece had an almost equal number of data points (i.e., the number of notes, the number of intervals between notes) for each dependent variable. The modified piece consisted of a 12-measure isochronous melody notated in 4/4 meter to be played with the right hand only. Two expressive notations (i.e., articulation and dynamics) were added, as shown in *Fig \ref{fig:stim}*.

@@

As predicted, experts produced longer legato when listening to the recordings where articulation was not implemented (*Fig \ref{fig:kot-1}*, left). Accordingly, there was a significant main effect of Articulation (*F*(`r leg_all_aov$anova_table[1,1]`, `r leg_all_aov$anova_table[1,2]`) = `r leg_all_aov$anova_table[1,4]`, *p* `r if(leg_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', leg_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[1,5])`). There was no significant main effect of Dynamics (*F*(`r leg_all_aov$anova_table[2,1]`, `r leg_all_aov$anova_table[2,2]`) = `r leg_all_aov$anova_table[2,4]`, *p* `r if(leg_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[2,5])`) and no significant interaction between Articulation and Dynamics (*F*(`r leg_all_aov$anova_table[3,1]`, `r leg_all_aov$anova_table[3,2]`) = `r leg_all_aov$anova_table[3,4]`, *p* `r if(leg_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', leg_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', leg_all_aov$anova_table[3,5])`).

@@

```{r kot-plot-1, include = FALSE}
leg_all_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  geom_signif(
    comparisons = list(c("Present", "Absent")),
    y_position = 120, tip_length = 0, textsize = 10, color = "black",
    annotation = c("*"),
  ) +
  labs(y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-20, 140, 40), limits = c(-20, 140)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

sta_all_plot <- ggplot(kot[Subcomponent1 == "Staccato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  geom_signif(
    comparisons = list(c("Present", "Absent")),
    y_position = -140, tip_length = 0, textsize = 10, color = "black",
    annotation = c("*"),
  ) +
  labs(y = "KOT (ms)", title = "KOT - Staccato") + scale_y_continuous(breaks = seq(-280, -120, 40), limits = c(-280, -120)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

Unlike our prediction, experts did not change their performances in terms of notated forte depending on the type of recordings (*Fig \ref{fig:vel-1}*, left). Neither the main effect of Articulation (*F*(`r for_all_aov$anova_table[1,1]`, `r for_all_aov$anova_table[1,2]`) = `r for_all_aov$anova_table[1,4]`, *p* `r if(for_all_aov$anova_table[1,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[1,6]))}`, $\eta_G^2$ = `r sprintf('%.2f', for_all_aov$anova_table[1,5])`) nor the main effect of Dynamics (*F*(`r for_all_aov$anova_table[2,1]`, `r for_all_aov$anova_table[2,2]`) = `r for_all_aov$anova_table[2,4]`, *p* `r if(for_all_aov$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[2,5])`) nor the interaction between Articulation and Dynamics was significant (*F*(`r for_all_aov$anova_table[3,1]`, `r for_all_aov$anova_table[3,2]`) = `r for_all_aov$anova_table[3,4]`, *p* `r if(for_all_aov$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', for_all_aov$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', for_all_aov$anova_table[3,5])`).

@@

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are intending to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., expert pianists should modulate their performance relevant to articulation, but not dynamics).

@@

Artificial recordings were generated from performance data that we obtained in our previous study [@tominaga_2022]. We used the data from Experiment 2. In Experiment 2, participants were asked to memorise one piece of music (*Fig 5* (A), @tominaga_2022) without any expressive notation before coming to the experiment. First, we asked participants to perform the memorised piece before starting the experiment to measure their baseline performance. After measuring the baseline performance, participants were asked to perform the piece with either articulation (*Fig 5* (B), @tominaga_2022) or dynamics (*Fig 5* (C), @tominaga_2022) in two conditions (teaching vs. performing). Here, we only used the data from the performing condition to make sure that the performances that we used did not have any particular modulations because of teaching intentions. Therefore, there were two types of performance data (articulation performance: performances played with notated articulation, dynamics performance: performances played with notated dynamics). We obtained 31 valid performances (i.g., performances without pitch errors) as baseline performances, 137 valid performances as articulation performances and 139 valid performances as dynamics performances.

@@

We aimed to generate four types of recordings and each type (i.e., both, art only, dyn only, none) had four instances (see *Apparatus and stimuli*) by using the performance data from @tominaga_2022. First, 16 instances for each type were generated. Second, for each type, we chose the four best instances, which exhibited the characteristic of each type well.

### 2023-01-16 paper/manuscript.tex
update figures / reflected feedback
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Effective teaching involves experts and novices dynamically interacting with each other (Byrne \& Rapaport, 2011). First, experts demonstrate what novices are meant to acquired and then novices attempt to reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities (Mermelshtine, 2017). This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by identifying novices' specific problems of each novice from their unsuccessful attempts and modifying their behaviour accordingly (Ugur, Nagai, Celikkanat, \& Oztop, 2015; Zukow-Goldring \& Arbib, 2007).

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions (Pezzulo et al., 2019), including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared to when they were demonstrating to adults (Brand, Baldwin, \& Ashburn, 2002).Such pedagogical action modulations are sensitive to the skill level of learners. For instance, evidence from parental scaffolding research suggests that caregivers scaffold infants' learning when the infants failed to produce an expected action (Wood \& Middleton, 1975; Zukow-Goldring \& Arbib, 2007). Fukuyama et al. (2015) performed a study, where mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups of different colours and sizes. Mothers demonstrated how to stack and fit the nesting cups with the intention to teach their infants to reproduce the actions by themselves. It was found that the mothers dynamically modulated their demonstrations according to the infants' object manipulation skills. Specifically, mothers exaggerated their movements when their infants failed to produce expected actions but did not produce such exaggerations when their infants lacked the motor skills needed to produce the required actions. Movement exaggerations for the purpose of teaching are observed not only towards infant learners but also when knowledgeable adults are interacting with adult learners (McEllin, Knoblich, \& Sebanz, 2017). For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own. However, it has not been established whether and how experts teaching skills to adult learners adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga, Knoblich, \& Sebanz, 2022), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To gain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., in press). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

The recorded performances serving as stimuli were all of one piece of music that had already been used in our previous study (Tominaga et al., in press). The piece was an excerpt from Clementi's Sonatina Op.36 (No.3) in C major. The first 12 measures of the original piece were used and modified so that the piece had an almost equal number of data points (i.e., the number of notes, the number of intervals between notes) for each dependent variable. The modified piece consisted of a 12-measure isochronous melody notated in 4/4 meter to be played with the right hand only. Two expressive notations (i.e., articulation and dynamics) were added, as shown in \emph{Fig \ref{fig:stim}}.

@@

As predicted, experts produced longer legato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, left). Accordingly, here was a significant main effect of Articulation (\emph{F}(1, 19) = 5.59, \emph{p} = 0.029, \(\eta_G^2\) = 0.002). There was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.06, \emph{p} = 0.81, \(\eta_G^2\) = 0.000) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 1.89, \emph{p} = 0.19, \(\eta_G^2\) = 0.002).

@@

Unlike our prediction, experts did not change their performances in terms of notated forte depending on the type of recordings (\emph{Fig \ref{fig:vel-1}}, left). Neither the main effect of Articulation (\emph{F}(1, 19) = 1.66, \emph{p} = 0.213, \(\eta_G^2\) = 0.00) nor the main effect of Dynamics (\emph{F}(1, 19) = 0.33, \emph{p} = 0.57, \(\eta_G^2\) = 0.000) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.00, \emph{p} = 0.96, \(\eta_G^2\) = 0.000).

@@

Artificial recordings were generated from performance data that we obtained in our previous study (Tominaga et al., in press). We used the data from Experiment 2. In Experiment 2, participants were asked to memorise one piece of music (\emph{Fig 5} (A), Tominaga et al., in press) without any expressive notation before coming to the experiment. First, we asked participants to perform the memorised piece before starting the experiment to measure their baseline performance. After measuring the baseline performance, participants were asked to perform the piece with either articulation (\emph{Fig 5} (B), Tominaga et al., in press) or dynamics (\emph{Fig 5} (C), Tominaga et al., in press) in two conditions (teaching vs.~performing). Here, we only used the data from the performing condition to make sure that the performances that we used did not have any particular modulations because of teaching intentions. Therefore, there were two types of performance data (articulation performance: performances played with notated articulation, dynamics performance: performances played with notated dynamics). We obtained 31 valid performances (i.g., performances without pitch errors) as baseline performances, 137 valid performances as articulation performances and 139 valid performances as dynamics performances.

@@

We aimed to generate four types of recordings and each type (i.e., both, art only, dyn only, none) had four instances (see \emph{Apparatus and stimuli}) by using the performance data from Tominaga et al (in press). First, 16 instances for each type were generated. Second, for each type, we chose the four best instances, which exhibited the characteristic of each type well.

>>>>

Effective teaching involves experts and novices dynamically interacting with each other (Byrne \& Rapaport, 2011). First, experts demonstrate what novices are meant to acquire and then novices attempt to reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities (Mermelshtine, 2017). This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by identifying novices' specific problems from their unsuccessful attempts and modifying their behaviour accordingly (Ugur, Nagai, Celikkanat, \& Oztop, 2015; Zukow-Goldring \& Arbib, 2007).

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions (Pezzulo et al., 2019), including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and to produce wide and expansive movements compared to when they were demonstrating to adults (Brand, Baldwin, \& Ashburn, 2002). Such pedagogical action modulations are sensitive to the skill level of learners. For instance, evidence from parental scaffolding research suggests that caregivers scaffold infants' learning when the infants failed to produce an expected action (Wood \& Middleton, 1975; Zukow-Goldring \& Arbib, 2007). Fukuyama et al. (2015) performed a study, where mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups of different colours and sizes. Mothers demonstrated how to stack and fit the nesting cups with the intention to teach their infants to reproduce the actions by themselves. It was found that mothers dynamically modulated their demonstrations according to the infants' object manipulation skills. Specifically, mothers exaggerated their movements when their infants failed to produce expected actions but did not produce such exaggerations when their infants lacked the motor skills to produce the required actions. Movement exaggerations for the purpose of teaching are observed not only towards infant learners but also when knowledgeable adults are interacting with adult learners (McEllin, Knoblich, \& Sebanz, 2017). For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own. However, it has not been established whether and how experts teaching skills to adult learners adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on learners' skill level. In our previous research (Tominaga, Knoblich, \& Sebanz, 2022), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To obtain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., 2022). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

The recorded performances serving as stimuli were all of one piece of music that had already been used in our previous study (Tominaga et al., 2022). The piece was an excerpt from Clementi's Sonatina Op.36 (No.3) in C major. The first 12 measures of the original piece were used and modified so that the piece had an almost equal number of data points (i.e., the number of notes, the number of intervals between notes) for each dependent variable. The modified piece consisted of a 12-measure isochronous melody notated in 4/4 meter to be played with the right hand only. Two expressive notations (i.e., articulation and dynamics) were added, as shown in \emph{Fig \ref{fig:stim}}.

@@

As predicted, experts produced longer legato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, left). Accordingly, there was a significant main effect of Articulation (\emph{F}(1, 19) = 5.59, \emph{p} = 0.029, \(\eta_G^2\) = 0.002). There was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.06, \emph{p} = 0.81, \(\eta_G^2\) = 0.000) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 1.89, \emph{p} = 0.19, \(\eta_G^2\) = 0.002).

@@

Unlike our prediction, experts did not change their performances in terms of notated forte depending on the type of recordings (\emph{Fig \ref{fig:vel-1}}, left). Neither the main effect of Articulation (\emph{F}(1, 19) = 1.66, \emph{p} = 0.21, \(\eta_G^2\) = 0.00) nor the main effect of Dynamics (\emph{F}(1, 19) = 0.33, \emph{p} = 0.57, \(\eta_G^2\) = 0.000) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.00, \emph{p} = 0.96, \(\eta_G^2\) = 0.000).

@@

Artificial recordings were generated from performance data that we obtained in our previous study (Tominaga et al., 2022). We used the data from Experiment 2. In Experiment 2, participants were asked to memorise one piece of music (\emph{Fig 5} (A), Tominaga et al. (2022)) without any expressive notation before coming to the experiment. First, we asked participants to perform the memorised piece before starting the experiment to measure their baseline performance. After measuring the baseline performance, participants were asked to perform the piece with either articulation (\emph{Fig 5} (B), Tominaga et al. (2022)) or dynamics (\emph{Fig 5} (C), Tominaga et al. (2022)) in two conditions (teaching vs.~performing). Here, we only used the data from the performing condition to make sure that the performances that we used did not have any particular modulations because of teaching intentions. Therefore, there were two types of performance data (articulation performance: performances played with notated articulation, dynamics performance: performances played with notated dynamics). We obtained 31 valid performances (i.g., performances without pitch errors) as baseline performances, 137 valid performances as articulation performances and 139 valid performances as dynamics performances.

@@

We aimed to generate four types of recordings and each type (i.e., both, art only, dyn only, none) had four instances (see \emph{Apparatus and stimuli}) by using the performance data from Tominaga et al. (2022). First, 16 instances for each type were generated. Second, for each type, we chose the four best instances, which exhibited the characteristic of each type well.
